---
title: "Social Media Activists"
author: "Aanchal Setia"
desription: "Initial Data Cleaning"
date: "10/10/2022"
format:
  html:
    toc: true
    code-fold: true
    code-copy: true
    code-tools: true
categories:
  - blog post II
  - Aanchal Setia
  
---

Summary of My Results:

I have scraped tweets from three different accounts: BLM NYC, BLM LA, and
BLM Chicago so far. 

Pre-processing
I created Wordclouds to understand the words that were redundant. 
I found that there were a lot of mentions of different accounts 
which were not useful for my research  question, so I removed them.
I also removed hashtags, numbers, emojis, punctuation, links, the phrase "rt",
and I changed all letters to lower case.


Basic Analysis Plan
Now that I have formatted tweets from three different chapters, I will run 
sentiment analysis on three different chapters and compare them.




```{r}
#| label: setup
#| warning: false

library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)
```


#Calling Necessary Libraries
```{R}
library(httr)
library(tm)
library(stringr)
library(rtweet)
library(twitteR)
library(purrr)
library(tidytext)
library(dplyr)
library(tidyr)
library(lubridate)
library(scales)
library(broom)
library(ggplot2)
library(quanteda)
library(quanteda.textplots)


```
#Getting Twitter Access
```{r}
consumerkey = ""
consumersecret = ""
accesstoken = ""
accesssecret = ""

options(httr_oauth_cache = T)
setup_twitter_oauth(consumer_key = consumerkey, consumer_secret = consumersecret,
                    access_token = accesstoken, access_secret = accesssecret)
```
#Set up default authentication for rtweet package
```{R}
auth_setup_default()
```

```{r}
##Creating a function to format tweets

formatting_tweets <- function(tweets)
{
  #Removing mentions
  tweets$full_text <-str_remove_all(string = tweets$full_text, 
                                    pattern = "[@][\\w_-]+" )
  #Removing hashtags
  tweets$full_text <-str_remove_all(string = tweets$full_text, 
                                    pattern = "[#][\\w_-]+" )
  #Removing Links
  tweets$full_text <-str_remove_all(string = tweets$full_text,
                                    pattern = "http\\S+\\s*" )
  #Removing Emojis
  tweets$full_text <- iconv(x = tweets$full_text, from = "latin1",
                            to = "ASCII", sub = "")
  #Removing Punctuations
  tweets$full_text <- str_remove_all(string = tweets$full_text, 
                                     pattern = "[[:punct:]]")
  #Changing Case to Lower Case
  tweets$full_text <- str_to_lower(string = tweets$full_text)
  #Removing Numbers
  tweets$full_text <- str_remove_all(string = tweets$full_text, 
                                     pattern = "[:digit:]")
  #Removing stopwords
  tweets$full_text <- removeWords(tweets$full_text,
                                  c(stopwords("en"), "can", "will"))
  #Now, I will remove "rt" from the text
  tweets$full_text <- gsub("^(rt)","",tweets$full_text)
  tweets$full_text  <-  gsub("amp", "", tweets$full_text) 
  #Removing Repeated Whitespace
  tweets$full_text <- str_squish(string = tweets$full_text)
  #Changing the format of time
  tweets$created_at <- format(tweets$created_at, format = "%Y")
  
  return(tweets)
}

```

```{R}
#Scraping Tweets from BLack Lives Matter's Three Chapters

BLMchapters <- c("BLMNYC",  "BLMChi", "BLMLA")


for (i in BLMchapters) {
  handle <- gsub(" ", "", paste("@", i))
  result <-  get_timeline(use = handle, n = 1) 
  formatted_result <- formatting_tweets(result)
  
  df_name <- i
  assign(df_name, data.frame(formatted_result))
}

```




