---
title: "Blog Post Four"
author: "Molly Hackbarth"
description: "Working with the data"
date: "10/29/2022"
format:
  html:
    toc: true
    code-fold: true
    code-copy: true
    code-tools: true
categories:
  - blog posts
  - hw4
  - molly hackbarth
---

```{r}
#| label: setup
#| warning: false

library(tidyverse)
library(cld3)
library(plyr)
library(dplyr)
library(stringi)
library(stringr)
library(here)
library(devtools)
library(tidytext)
library(quanteda)
library(quanteda.textstats)
library(quanteda.textmodels)
library(quanteda.textplots)
library(wordcloud)
library(tm)
library(emojifont)
#new packages
library(devtools)
#devtools::install_github("kbenoit/quanteda.dictionaries") 
library(quanteda.dictionaries)
#devtools::install_github("quanteda/quanteda.sentiment")
library(quanteda.sentiment)


knitr::opts_chunk$set(echo = TRUE)
```

# Research Question

**My current research question:** How do Reddit and Twitter users feel about the show *Love is Blind Japan*?

# Reading in the Data

```{r reading data}
#write csv has been commented out due to it continously trying to save an "updated version" in Git. 

reddit_data <- read.csv(here::here("posts", "_data", "loveisblindjapan.csv"))

twitter1 <- read.csv(here::here("posts", "_data", "tweets.csv"))

twitter2 <- read.csv(here::here("posts", "_data", "tweets#.csv"))

reddit <- subset(reddit_data, select = c("body", "created_utc")) 

reddit$created_utc <- as.Date.POSIXct(reddit$created_utc)

reddit <- reddit %>% 
  select(text = body, 
            date = created_utc)
# remove deleted or removed comments by moderators of the subreddit (ones that only contain [deleted] or [removed])
reddit <- reddit %>% 
  filter(!text == '[deleted]') %>% 
  filter(!text == '[removed]')

#remove counting column
twitter1 <- twitter1 %>% select(!c(X, User))
twitter2 <- twitter2 %>% select(!c(X, User))

twitter <- merge(twitter1, twitter2, by=c('Tweet','Tweet', 'Date', 'Date'),all=T, ignore_case =T)
#write.csv(twitter, here::here("posts", "_data", "twitter.csv") , all(T) )

names(twitter) <- tolower(names(twitter))
twitter <- twitter %>% 
  rename_at('tweet', ~ 'text', 
            'Date' ~ 'date')
twitter$date <- as.Date(strftime(twitter$date, format="%Y-%m-%d"))

# remove duplicate tweets
twitter <- twitter %>% distinct(text, date, .keep_all = TRUE)

#check for duplicate tweets
twitter %in% unique(twitter[ duplicated(twitter)]) 

allsocialmedia <- merge(twitter, reddit, by=c('text','text', 'date', 'date'),all=T, ignore_case =T)
#write.csv(twitter, here::here("posts", "_data", "loveisblind_socialmedia.csv") , all(T) )
```

# Creating a Separate Word Cloud for Twitter

In order to remove the dates from Twitter I decided to run the same formula only on the Twitter text column.

```{r twitter text word cloud}
twitter_text <- twitter$text
twitter_text_corpus <- subset(twitter_text, detect_language(twitter) == "en")
twitter_text_corpus <- twitter_text_corpus[!is.na(twitter_text_corpus)]
twitter_text_corpus <- corpus(twitter_text_corpus)
twittertextsummary <- summary(twitter_text_corpus)

twitter_text_corpus_tokens <- tokens(twitter_text_corpus, 
    remove_punct = T,
    remove_numbers = T,
    remove_symbols = T,
    remove_url = T) %>% 
  tokens_tolower() %>% 
  tokens_select(pattern = stopwords("en"), selection = "remove")

twitter_text_lemmitized <- tokens_replace(twitter_text_corpus_tokens, 
                             pattern = lexicon::hash_lemmas$token, 
                             replacement = lexicon::hash_lemmas$lemma)

library(quanteda.textplots)
twitter_corpus_text_dfm <- twitter_text_lemmitized %>% 
  dfm() %>% 
  dfm_remove(stopwords('english')) %>% 
  dfm_trim(min_termfreq = 30, verbose = FALSE)

textplot_wordcloud(twitter_corpus_text_dfm, max_words=200, color="blue")

```

## Removing The Show's Name

Although the data is a lot cleaner now I do wonder if removing the key words "love", "blind", "japan" and "#loveisblindjapan" will give a better picture of how posters are feeling. I will go ahead and remove the phrases.

```{r removing the shows title}

twitter_text <- twitter$text

twitter_text_corpus <- subset(twitter_text, detect_language(twitter) == "en")
twitter_text_corpus <- twitter_text_corpus[!is.na(twitter_text_corpus)]
twitter_text_corpus <- corpus(twitter_text_corpus)
twittertextsummary <- summary(twitter_text_corpus)

mystopwords <- c("love is blind japan", "#loveisbindjapan", "#LoveIsBlindJapan","Love Is Blind Japan","Love is Blind Japan", "Love Is Blind: Japan", "#loveisblind", "ラブイズブラインドjapan", "#ラブイズブラインドjapan", "loveisblind", "#loveisblind2", "blind:japan")

twitter_text_corpus_tokens <- tokens(twitter_text_corpus, 
    remove_punct = T,
    remove_numbers = T,
    remove_symbols = T,
    remove_url = T) %>% 
  tokens_tolower() %>% 
  tokens_remove(pattern = phrase(mystopwords), valuetype = 'fixed') %>% 
  tokens_select(pattern = stopwords("en"), selection = "remove")

twitter_text_lemmitized <- tokens_replace(twitter_text_corpus_tokens, 
                             pattern = lexicon::hash_lemmas$token, 
                             replacement = lexicon::hash_lemmas$lemma)

library(quanteda.textplots)
twitter_corpus_text_dfm <- twitter_text_lemmitized %>% 
  dfm() %>% 
  dfm_remove(stopwords('english')) %>% 
  dfm_trim(min_termfreq = 30, verbose = FALSE)

textplot_wordcloud(twitter_corpus_text_dfm, max_words=200, color="blue")

```

Here is we can see a more accurate idea of how people are tweeting about the show. Even with the show's title being remove love is still a large part of tweets.

I also noticed that "blind" was used often. Looking at the tweets it seems unlikely that the word blind was used in any other way than to mention the show. Thus I'd like to remove the word blind as well since it seems unlikely to be useful to sentiment analysis.

I will also remove the word "show" as show seemingly is only talking about the series rather than any emotions.

```{r removing the words blind and show}
twitter_text <- twitter$text

twitter_text_corpus <- subset(twitter_text, detect_language(twitter) == "en")
twitter_text_corpus <- twitter_text_corpus[!is.na(twitter_text_corpus)]
twitter_text_corpus <- corpus(twitter_text_corpus)
twittertextsummary <- summary(twitter_text_corpus)

mystopwords <- c("love is blind japan", "#loveisbindjapan", "#LoveIsBlindJapan","Love Is Blind Japan","Love is Blind Japan", "Love Is Blind: Japan", "#loveisblind", "ラブイズブラインドjapan", "#ラブイズブラインドjapan", "loveisblind", "#loveisblind2", "blind:japan", "blind", "show")

twitter_text_corpus_tokens <- tokens(twitter_text_corpus, 
    remove_punct = T,
    remove_numbers = T,
    remove_symbols = T,
    remove_url = T) %>% 
  tokens_tolower() %>% 
  tokens_remove(pattern = phrase(mystopwords), valuetype = 'fixed') %>% 
  tokens_select(pattern = stopwords("en"), selection = "remove")

twitter_text_lemmitized <- tokens_replace(twitter_text_corpus_tokens, 
                             pattern = lexicon::hash_lemmas$token, 
                             replacement = lexicon::hash_lemmas$lemma)

library(quanteda.textplots)
twitter_corpus_text_dfm <- twitter_text_lemmitized %>% 
  dfm() %>% 
  dfm_remove(stopwords('english')) %>% 
  dfm_trim(min_termfreq = 30, verbose = FALSE)

textplot_wordcloud(twitter_corpus_text_dfm, max_words=200, color="blue")

```

# Reddit and Updated Social Media word cloud

```{r reddit word cloud same}

reddit_corpus <- subset(reddit, detect_language(reddit) == "en")
reddit_corpus <- reddit_corpus[!is.na(reddit_corpus)]
reddit_corpus <- corpus(reddit)
redditsummary <- summary(reddit_corpus)

reddit_corpus_tokens <- tokens(reddit_corpus, 
    remove_punct = T,
    remove_numbers = T, 
    remove_symbols = T,
    remove_url = T) %>% 
  tokens_tolower() %>% 
  tokens_select(pattern = stopwords("en"), selection = "remove")

reddit_lemmitized <- tokens_replace(reddit_corpus_tokens, 
                             pattern = lexicon::hash_lemmas$token, 
                             replacement = lexicon::hash_lemmas$lemma)

library(quanteda.textplots)

reddit_corpus_dfm <- reddit_lemmitized %>% 
  dfm() %>% 
  dfm_remove(stopwords('english')) %>% 
  dfm_trim(min_termfreq = 30, verbose = FALSE)

textplot_wordcloud(reddit_corpus_dfm, max_words=200, color="red")

```

```{r social updated word cloud}

social_corpus <- subset(allsocialmedia, detect_language(allsocialmedia) == "en")
social_corpus <- corpus(social_corpus)
socialsummary <- summary(social_corpus)

social_corpus <- social_corpus[!is.na(social_corpus)]


mystopwords <- c("love is blind japan", "#loveisbindjapan", "#LoveIsBlindJapan","Love Is Blind Japan","Love is Blind Japan", "Love Is Blind: Japan", "#loveisblind", "ラブイズブラインドjapan", "#ラブイズブラインドjapan", "loveisblind", "#loveisblind2", "blind:japan")

social_corpus_tokens <- tokens(social_corpus, 
    remove_punct = T,
    remove_numbers = T,
    remove_symbols = T,
    remove_url = T) %>% 
  tokens_tolower() %>% 
  tokens_remove(pattern = phrase(mystopwords), valuetype = 'fixed') %>% 
  tokens_select(pattern = stopwords("en"), selection = "remove")

social_lemmitized <- tokens_replace(social_corpus_tokens, 
                             pattern = lexicon::hash_lemmas$token, 
                             replacement = lexicon::hash_lemmas$lemma)

library(quanteda.textplots)

social_corpus_dfm <- social_lemmitized %>% 
  dfm() %>% 
  dfm_remove(stopwords('english')) %>% 
  dfm_trim(min_termfreq = 30, verbose = FALSE)

textplot_wordcloud(social_corpus_dfm, max_words=200, color="orange")
```

# Dictionary Approach with Twitter

I will now try the dictionary approach using reddit, twitter, and the data combined (allsocialmedia).

```{r review sentiment twitter}
twitterDfm_nrc <- dfm(tokens(twitter_text_lemmitized,
                              remove_punct = TRUE),
                       tolower = TRUE) %>%
                    dfm_lookup(data_dictionary_NRC)

dim(twitterDfm_nrc)
twitterDfm_nrc

tdf_nrc <- convert(twitterDfm_nrc, to = "data.frame")
tdf_nrc$polarity <- (tdf_nrc$positive - tdf_nrc$negative)/(tdf_nrc$positive + tdf_nrc$negative)
tdf_nrc$polarity[which((tdf_nrc$positive + tdf_nrc$negative) == 0)] <- 0

ggplot(tdf_nrc) + 
  geom_histogram(aes(x=polarity)) + 
  theme_bw()

```

Here we can see that for twitter most people were more positive about the show! That does correlate from what I often saw from skimming the tweets.

Still we should double check to make sure that these actually do skew positively.

```{r comparing dictionaries twitter}

# convert corpus to DFM using the LSD2015 dictionary
twitterDfm_lsd2015 <- dfm(tokens(twitter_text_lemmitized, remove_punct = TRUE),
                              tolower = TRUE) %>%
                          dfm_lookup(data_dictionary_LSD2015)

# convert corpus to DFM using the General Inquirer dictionary
twitterDfm_geninq <- dfm(tokens(twitter_text_lemmitized, remove_punct = TRUE),
                             tolower = TRUE) %>%
                    dfm_lookup(data_dictionary_geninqposneg)

# create polarity measure for LSD2015
tdf_lsd2015 <- convert(twitterDfm_lsd2015, to = "data.frame")
tdf_lsd2015$polarity <- (tdf_lsd2015$positive - tdf_lsd2015$negative)/(tdf_lsd2015$positive + tdf_lsd2015$negative)
tdf_lsd2015$polarity[which((tdf_lsd2015$positive + tdf_lsd2015$negative) == 0)] <- 0

# look at first few rows
head(df_lsd2015)

# create polarity measure for GenInq
tdf_geninq <- convert(twitterDfm_geninq, to = "data.frame")
tdf_geninq$polarity <- (tdf_geninq$positive - tdf_geninq$negative)/(tdf_geninq$positive + tdf_geninq$negative)
tdf_geninq$polarity[which((tdf_geninq$positive + tdf_geninq$negative) == 0)] <- 0

# look at first few rows
head(tdf_geninq)

# create unique names for each dataframe
colnames(tdf_nrc) <- paste("nrc", colnames(tdf_nrc), sep = "_")
colnames(tdf_lsd2015) <- paste("lsd2015", colnames(tdf_lsd2015), sep = "_")
colnames(tdf_geninq) <- paste("geninq", colnames(tdf_geninq), sep = "_")

# now let's compare our estimates
tsent_df <- merge(tdf_nrc, tdf_lsd2015, by.x = "nrc_doc_id", by.y = "lsd2015_doc_id")
tsent_df <- merge(tsent_df, tdf_geninq, by.x = "nrc_doc_id", by.y = "geninq_doc_id")

head(tsent_df)

cor(tsent_df$nrc_polarity, tsent_df$lsd2015_polarity)

cor(tsent_df$nrc_polarity, tsent_df$geninq_polarity)

cor(tsent_df$lsd2015_polarity, tsent_df$geninq_polarity)

# Plot these out. You can update this to check the look of other combinations
ggplot(tsent_df, mapping = aes(x=nrc_polarity, y=lsd2015_polarity)) + 
  geom_point(alpha = 0.1) +
  geom_smooth() +
  geom_abline(intercept=0,slope=1, color = "red") +
  theme_bw()
```

Interestingly it seems there is a good amount of correlation between the two. Although not as strong as the tutorial it does seem that the dictionary is fairly accuarte. Let's test this for both reddit and allsocialmedia.

```{r reddit dictionary}

redditDfm_nrc <- dfm(tokens(reddit_lemmitized,
                              remove_punct = TRUE),
                       tolower = TRUE) %>%
                    dfm_lookup(data_dictionary_NRC)

dim(redditDfm_nrc)
redditDfm_nrc

rdf_nrc <- convert(redditDfm_nrc, to = "data.frame")
rdf_nrc$polarity <- (rdf_nrc$positive - rdf_nrc$negative)/(rdf_nrc$positive + rdf_nrc$negative)
rdf_nrc$polarity[which((rdf_nrc$positive + rdf_nrc$negative) == 0)] <- 0

ggplot(rdf_nrc) + 
  geom_histogram(aes(x=polarity)) + 
  theme_bw()

```

```{r reddit sentiment}

rdf_nrc <- convert(redditDfm_nrc, to = "data.frame")
rdf_nrc$polarity <- (rdf_nrc$positive - rdf_nrc$negative)/(rdf_nrc$positive + rdf_nrc$negative)
rdf_nrc$polarity[which((rdf_nrc$positive + rdf_nrc$negative) == 0)] <- 0

ggplot(rdf_nrc) + 
  geom_histogram(aes(x=polarity)) + 
  theme_bw()


# convert corpus to DFM using the LSD2015 dictionary
redditDfm_lsd2015 <- dfm(tokens(reddit_lemmitized, remove_punct = TRUE),
                              tolower = TRUE) %>%
                          dfm_lookup(data_dictionary_LSD2015)

# convert corpus to DFM using the General Inquirer dictionary
redditDfm_geninq <- dfm(tokens(reddit_lemmitized, remove_punct = TRUE),
                             tolower = TRUE) %>%
                    dfm_lookup(data_dictionary_geninqposneg)

# create polarity measure for LSD2015
rdf_lsd2015 <- convert(redditDfm_lsd2015, to = "data.frame")
rdf_lsd2015$polarity <- (rdf_lsd2015$positive - rdf_lsd2015$negative)/(rdf_lsd2015$positive + rdf_lsd2015$negative)
rdf_lsd2015$polarity[which((rdf_lsd2015$positive + rdf_lsd2015$negative) == 0)] <- 0

# look at first few rows
head(rdf_lsd2015)

# create polarity measure for GenInq
rdf_geninq <- convert(redditDfm_geninq, to = "data.frame")
rdf_geninq$polarity <- (rdf_geninq$positive - rdf_geninq$negative)/(rdf_geninq$positive + rdf_geninq$negative)
rdf_geninq$polarity[which((rdf_geninq$positive + rdf_geninq$negative) == 0)] <- 0

# look at first few rows
head(rdf_geninq)

# create unique names for each dataframe
colnames(rdf_nrc) <- paste("nrc", colnames(rdf_nrc), sep = "_")
colnames(rdf_lsd2015) <- paste("lsd2015", colnames(rdf_lsd2015), sep = "_")
colnames(rdf_geninq) <- paste("geninq", colnames(rdf_geninq), sep = "_")

# now let's compare our estimates
rsent_df <- merge(rdf_nrc, rdf_lsd2015, by.x = "nrc_doc_id", by.y = "lsd2015_doc_id")
rsent_df <- merge(rsent_df, rdf_geninq, by.x = "nrc_doc_id", by.y = "geninq_doc_id")

head(rsent_df)

cor(rsent_df$nrc_polarity, rsent_df$lsd2015_polarity)

cor(rsent_df$nrc_polarity, rsent_df$geninq_polarity)

cor(rsent_df$lsd2015_polarity, rsent_df$geninq_polarity)

# Plot these out. You can update this to check the look of other combinations
ggplot(rsent_df, mapping = aes(x=nrc_polarity, y=lsd2015_polarity)) + 
  geom_point(alpha = 0.1) +
  geom_smooth() +
  geom_abline(intercept=0,slope=1, color = "red") +
  theme_bw()

```

```{r social media dictionary}

socialDfm_nrc <- dfm(tokens(social_lemmitized,
                              remove_punct = TRUE),
                       tolower = TRUE) %>%
                    dfm_lookup(data_dictionary_NRC)

dim(socialDfm_nrc)
socialDfm_nrc

df_nrc <- convert(socialDfm_nrc, to = "data.frame")
df_nrc$polarity <- (df_nrc$positive - df_nrc$negative)/(df_nrc$positive + df_nrc$negative)
df_nrc$polarity[which((df_nrc$positive + df_nrc$negative) == 0)] <- 0

ggplot(df_nrc) + 
  geom_histogram(aes(x=polarity)) + 
  theme_bw()

```

```{r all social media sentiment}

# convert corpus to DFM using the LSD2015 dictionary
socialDfm_lsd2015 <- dfm(tokens(social_lemmitized, remove_punct = TRUE),
                              tolower = TRUE) %>%
                          dfm_lookup(data_dictionary_LSD2015)

# convert corpus to DFM using the General Inquirer dictionary
socialDfm_geninq <- dfm(tokens(social_lemmitized, remove_punct = TRUE),
                             tolower = TRUE) %>%
                    dfm_lookup(data_dictionary_geninqposneg)

# create polarity measure for LSD2015
df_lsd2015 <- convert(socialDfm_lsd2015, to = "data.frame")
df_lsd2015$polarity <- (df_lsd2015$positive - df_lsd2015$negative)/(df_lsd2015$positive + df_lsd2015$negative)
df_lsd2015$polarity[which((df_lsd2015$positive + df_lsd2015$negative) == 0)] <- 0

# look at first few rows
head(df_lsd2015)

# create polarity measure for GenInq
df_geninq <- convert(socialDfm_geninq, to = "data.frame")
df_geninq$polarity <- (df_geninq$positive - df_geninq$negative)/(df_geninq$positive + df_geninq$negative)
df_geninq$polarity[which((df_geninq$positive + df_geninq$negative) == 0)] <- 0

# look at first few rows
head(df_geninq)

# create unique names for each dataframe
colnames(df_nrc) <- paste("nrc", colnames(df_nrc), sep = "_")
colnames(df_lsd2015) <- paste("lsd2015", colnames(df_lsd2015), sep = "_")
colnames(df_geninq) <- paste("geninq", colnames(df_geninq), sep = "_")

# now let's compare our estimates
sent_df <- merge(df_nrc, df_lsd2015, by.x = "nrc_doc_id", by.y = "lsd2015_doc_id")
sent_df <- merge(sent_df, df_geninq, by.x = "nrc_doc_id", by.y = "geninq_doc_id")

head(sent_df)

cor(sent_df$nrc_polarity, sent_df$lsd2015_polarity)

cor(sent_df$nrc_polarity, sent_df$geninq_polarity)

cor(sent_df$lsd2015_polarity, sent_df$geninq_polarity)

# Plot these out. You can update this to check the look of other combinations
ggplot(sent_df, mapping = aes(x=nrc_polarity, y=lsd2015_polarity)) + 
  geom_point(alpha = 0.1) +
  geom_smooth() +
  geom_abline(intercept=0,slope=1, color = "red") +
  theme_bw()

```

Interestingly compared to Twitter, Reddit and "allsocialmedia" were a fair amount lower in correlation. Although it was still a fairly high correlation this may because of the different types of words used by Reddit.

However when you compare the graphs all three are nearly identical in nature.

# Final Thoughts (TLDR) Currently Last Week

## Final thoughts

-   I did end up looking at Youtube to see if there were clips of this show online that were from Netflix. There unfortunately only seemed to be a trailer for the show. Clips of this season were fairly rare there.

-   After debating for awhile I decided to use the subset language option to remove all other languages for Twitter (Reddit did not have this problem most likely due to the main user base being English speaking Americans). Although this did cut my database down significantly I believe this was the best option as it removes any other language that I'm currently unable to analyze properly.

    -   Conversely Reddit had very few other languages. However to keep the data similar I used subset for Reddit too.

        -   This was also done so if I would like to use both the separate data and the data combined it is the same.

-   I decided to use the quanteda.textplots for the word cloud instead of the TM package. This is due to the TM package having issues when I try to reload the word clouds.

-   I have decided to lemmitize my tokens as it works to create a more accurate picture of words that were important to both Twitter and Reddit posters.

-   I have removed emojis due to the issues of most of the emoji packages I have found not working. Additionally I'm not confident that I could accurately use them for a sentiment analysis, or that there are that many in the first place.

-   For my tokens I have added remove_symbols and remove_url for both Reddit and Twitter to help out with people spamming urls to shows or gifs, and the "\@" sign.

-   When I checked the top features it was interesting to see what words were used the most. While none of it was surprising, it did help me to understand the words a bit more.

-   I believe a co-occurance matrix may be useful for Twitter as it allows me to remove the name of the show and the hashtag better.

## Questions and frustrations I still have

-   I'm still unsure how to keep **both the date and the text** as separate columns using the corpus() function from quanteda. I can keep it in the summary, but I'm not sure if I can use the dates outside of that.

    -   The summary also only goes to 100, I'm not sure how I can make it show me all of the data either.
    -   When I tried having a maximum frequency for Twitter's word cloud it did bring out the dates in the word cloud but I'm not sure if that solves my problem either.

-   I am unsure if looking at all the data together or separately is currently the best. I have a word cloud using all the social media data below. This would change my research question.

    -   **Current Research Question:** How do Reddit and Twitter users feel about the show *Love is Blind Japan*?

    -   **Possibly Research Question:** How do Reddit and Twitter users sentiment differentiate about the show *Love is Blind Japan*?

        -   This is the question I had previously.

## Future Work

Here are a few things I'd like to do in blog post 4:

-   **Try to group by date.** With the date column seemingly working now I'd like to see if grouping by date would work.

-   **Try to use the textplot_network on reddit as well as the combined data set.** Although I'm not sure if I will I think it could produce some interesting results.

-   **Try to find a way to remove the dates from the word clouds.** My current thought is to just make a separate r chunk that only has twitter\$text to remove the dates.

-   **Try to decide on how or if I want to use co-occurrence.**

# Final Code

```{r reddit word cloud}
reddit_corpus <- subset(reddit, detect_language(reddit) == "en")
reddit_corpus <- reddit_corpus[!is.na(reddit_corpus)]
reddit_corpus <- corpus(reddit)
redditsummary <- summary(reddit_corpus)

reddit_corpus_tokens <- tokens(reddit_corpus, 
    remove_punct = T,
    remove_numbers = T, 
    remove_symbols = T,
    remove_url = T) %>% 
  tokens_tolower() %>% 
  tokens_select(pattern = stopwords("en"), selection = "remove")

reddit_lemmitized <- tokens_replace(reddit_corpus_tokens, 
                             pattern = lexicon::hash_lemmas$token, 
                             replacement = lexicon::hash_lemmas$lemma)

library(quanteda.textplots)

reddit_corpus_dfm <- reddit_lemmitized %>% 
  dfm() %>% 
  dfm_remove(stopwords('english')) %>% 
  dfm_trim(min_termfreq = 30, verbose = FALSE)

textplot_wordcloud(reddit_corpus_dfm, max_words=200, color="red")
```

```{r twitter word cloud}

twitter_corpus <- subset(twitter, detect_language(twitter) == "en")
twitter_corpus <- twitter_corpus[!is.na(twitter_corpus)]
twitter_corpus <- corpus(twitter_corpus)
twittersummary <- summary(twitter_corpus)

twitter_corpus_tokens <- tokens(twitter_corpus, 
    remove_punct = T,
    remove_numbers = T,
    remove_symbols = T,
    remove_url = T) %>% 
  tokens_tolower() %>% 
  tokens_select(pattern = stopwords("en"), selection = "remove")

twitter_lemmitized <- tokens_replace(twitter_corpus_tokens, 
                             pattern = lexicon::hash_lemmas$token, 
                             replacement = lexicon::hash_lemmas$lemma)

library(quanteda.textplots)
twitter_corpus_dfm <- twitter_lemmitized %>% 
  dfm() %>% 
  dfm_remove(stopwords('english')) %>% 
  dfm_trim(min_termfreq = 30, verbose = FALSE)

textplot_wordcloud(twitter_corpus_dfm, max_words=200, color="blue")
```

```{r full social media word cloud}

social_corpus <- subset(allsocialmedia, detect_language(allsocialmedia) == "en")
social_corpus <- corpus(social_corpus)
socialsummary <- summary(social_corpus)

social_corpus <- social_corpus[!is.na(social_corpus)]


mystopwords <- c("love is blind japan", "#loveisbindjapan", "#LoveIsBlindJapan","Love Is Blind Japan","Love is Blind Japan", "Love Is Blind: Japan", "#loveisblind", "ラブイズブラインドjapan", "#ラブイズブラインドjapan", "loveisblind", "#loveisblind2", "blind:japan")

social_corpus_tokens <- tokens(social_corpus, 
    remove_punct = T,
    remove_numbers = T,
    remove_symbols = T,
    remove_url = T) %>% 
  tokens_tolower() %>% 
  tokens_remove(pattern = phrase(mystopwords), valuetype = 'fixed') %>% 
  tokens_select(pattern = stopwords("en"), selection = "remove")

social_lemmitized <- tokens_replace(social_corpus_tokens, 
                             pattern = lexicon::hash_lemmas$token, 
                             replacement = lexicon::hash_lemmas$lemma)

library(quanteda.textplots)

social_corpus_dfm <- social_lemmitized %>% 
  dfm() %>% 
  dfm_remove(stopwords('english')) %>% 
  dfm_trim(min_termfreq = 30, verbose = FALSE)

textplot_wordcloud(social_corpus_dfm, max_words=200, color="orange")
```

```{r top features}
topfeatures(social_corpus_dfm, 10)
topfeatures(twitter_corpus_dfm, 10)
topfeatures(reddit_corpus_dfm, 10)
```

```{r cooccurrence}

# let's create a nicer dfm by limiting to words that appear frequently and are in more than 30% of chapters
smaller_dfm <- dfm_trim(twitter_corpus_dfm, max_termfreq = 3400, min_termfreq = 30)
smaller_dfm <- dfm_trim(smaller_dfm, max_docfreq = .3, docfreq_type = "prop")

textplot_wordcloud(smaller_dfm, min_count = 100,
                   random_order = FALSE)

# create fcm from dfm
smaller_fcm <- fcm(smaller_dfm)

# check the dimensions (i.e., the number of rows and the number of columnns)
# of the matrix we created
dim(smaller_fcm)

myFeatures <- names(topfeatures(smaller_fcm, 30))

# retain only those top features as part of our matrix
even_smaller_fcm <- fcm_select(smaller_fcm, pattern = myFeatures, selection = "keep")

# check dimensions
dim(even_smaller_fcm)

# compute size weight for vertices in network
size <- log(colSums(even_smaller_fcm))

# create plot
textplot_network(even_smaller_fcm, vertex_size = size / max(size) * 3)
```
