---
title: "Blog 3- Semantic Network Analysis"
author: "Rhowena Vespa"
desription: "TF-IDF/ dfm/Sematic Network Visualization"
date: "10/16/2022"
format:
  html:
    toc: true
    code-fold: true
    code-copy: true
    code-tools: true
categories:
  - Blog 3
  - Rhowena Vespa
  - Semantic Network Analysis
  - Twitter
  - TF-IDF
  - dfm
  - Text representation
---

```{r}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


```{r}
library(readr)
library(dplyr)
library(quanteda)
library(quanteda.textstats)
library(quanteda.textplots)
library(ggplot2)
library(DT)
library(tm)
library(stringr)
```

This 3rd Blog uses text representation concepts from week 6. Using tweet replies as corpus,
I will apply document-feature matrix and term-co-occurence matrix to better undersatnd the relationships of the texts.
I will also apply TF-IDF: Term Frequency-Inverse Document Frequency to rank the words by frequency.
Data visualization of the semantic network to understand what words co-occur with one another.

```{r}
# Read in data

IRA<- read_csv("IRA_med.csv")
#remove @twitter handles
IRA$text <- gsub("@[[:alpha:]]*","", IRA$text) #remove Twitter handles
```

```{r}
IRA_corpus <- corpus(IRA,text_field = "text")   
```

#tokenize and stemming
```{r}
IRA_tokens <- tokens(IRA_corpus)
IRA_tokens <- tokens_wordstem(IRA_tokens)
```
# Locate keywords in text
I played around with this and compared results from keywords :"inflation", "pharma", and "price".


```{r}
IRA_kw <- kwic(IRA_tokens, pattern =  "price*", window = 3,
  valuetype = c("glob", "regex", "fixed"),
  separator = " ",
  case_insensitive = TRUE,
  index = NULL) 
head(IRA_kw, 5) 
```
#TF-IDF rank words by term frequency


```{r}
IRA_dfm <- tokens(IRA_corpus, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_url=TRUE) %>%  
  tokens_remove (stopwords("en")) %>%
  dfm()
topfeatures(IRA_dfm) 

```

#rank words by TF-IDF



```{r}
IRA_dfm <- dfm_tfidf(IRA_dfm) 
topfeatures(IRA_dfm) 
```


#Keyness analysis as an alternative to tf-idf
I grouped the responses as based on possible sensitivity of the tweet replies. 
The possibly sensitive =TRUE replies "keywords" compared to the associations and a reference group of possible_sensitive= FALSE group replies,

```{r}
IRA_dfm <- tokens(IRA_corpus, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_url=TRUE) %>%
  dfm() %>%
  dfm_group(groups = possibly_sensitive)  

IRAkey <- textstat_keyness(IRA_dfm, target = "TRUE")
textplot_keyness(IRAkey,
  show_reference = TRUE,
  show_legend = TRUE,
  n = 20L,
  min_count = 2L,
  margin = 0.05,
  color = c("darkblue", "red"),
  labelcolor = "gray30",
  labelsize = 4,
  font = NULL
)
```
# DFM that contains hashtags 
```{r}
IRAtag_dfm <- dfm_select(IRA_dfm, pattern = "#*")
IRAtoptag <- names(topfeatures(IRA_dfm, 50)) 
head(IRAtoptag)
```

#Feature-occurrence matrix of hashtags

```{r}
IRAtag_fcm <- fcm(IRA_dfm)
head(IRAtag_fcm)
```

#Visualization of semantic network based on hashtag co-occurrence

```{r}
IRAtopgat_fcm <- fcm_select(IRAtag_fcm, pattern = IRAtoptag)
textplot_network(IRAtopgat_fcm, min_freq = 0.5,
  omit_isolated = TRUE,
  edge_color = "#1F78B4",
  edge_alpha = 0.5,
  edge_size = 2,
  vertex_color = "#4D4D4D",
  vertex_size = 2,
  vertex_labelcolor = NULL,
  vertex_labelfont = NULL,
  vertex_labelsize = 5,
  offset = NULL)
```
