---
title: "Text as Data Final Project"
author: "Ethan Campbell"
description: "Research into English Premier League and how language changes depending on the season"
date: "11/16/2022"
format:
  html:
    toc: true
    code-fold: true
    code-copy: true
    code-tools: true
categories:
  - Blog Post 2
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Packages

```{r}
#| warning: false
library(rvest)
library(tidyverse)
library(polite)
library(stringr)
library(preText)
library(quanteda)
library(quanteda.textplots)
library(tidytext)
library(tm)
library(SentimentAnalysis)
```

# Data Sources

There are 6 teams included in this study 2 from the top of the table 2 from the middle and 2 from the bottom. They are already in that order from top to bottom. Data needed to be web scraped from a page called match report. This page was located on each teams official website and this page included information about the match, statistics, and quotes from both the players and the managers. This data will include this current season and all of last season.

[Arsenal Data](https://www.arsenal.com/news?field_article_arsenal_team_value=men&revision_information=&page=1)

[Manchester City Data](https://www.mancity.com/news/mens)

[Newcastle United Data](https://www.nufc.co.uk/matches/first-team/#results)

[Everton Data](https://www.evertonfc.com/results)

[Leicester Data](https://www.lcfc.com/matches/reports)

[West Ham United Data](https://www.whufc.com/fixture/list/713)

# Hypothesis for project

::: callout-note
## Research Questions

A. Does Premier League soccer teams language change over the course of the season?

B. Does the language grow in correlation to the success of the season?
:::

The hypothesis will be tested as follows:

::: callout-tip
## H~0A~

The Premier league soccer team language [does not]{.underline} change over the course of the season.
:::

::: callout-tip
## H~1A~

The Premier league soccer team language [does]{.underline} change over the course of the season.
:::

::: callout-tip
## H~0A~

The language [does not]{.underline} correlate to the success of the season.
:::

::: callout-tip
## H~1A~

The language [does]{.underline} correlate to the success of the season.
:::

# Analytic planning

```{mermaid}
flowchart LR
  A[Web Scrape] --> B(Preprocess)
  B --> C[Organize]
  C --> D(TDM)
  D --> E[Sentiment Analysis]
  E --> F[Research Question 1]
  F --> G{Conclusion}
  D --> H[DTM]
  H --> I[Document Similarity]
  I --> J[Research Question 2]
  J --> G{Conclusion}
```

# Web Scraping/Tidying data

Here is the beginning of the web scraping process. I was unable to find a way to make the web scraper search for one object then proceed to the next page where you could then scrape whats inside. For the time being I decided to manually web scrape the information. The tidying process is the real issue as there are many unwanted variables inside. For example there are a lot of /n's.

```{r}
## The function is working at reading in the data however. parts of the cleaning process are failing and I am thinking this is because I am not specifying the create values

# I need to remove punct, capitalization, stopwords like (the, a ',') finish repeating the process to all teams and adjusting the function until it grabs every single problem once this is complete we should be able to tokenize then corpus and work with the data

Web_scrape_function_Arsenal <- function(url,css,data) { # creating function to repeat web scrape 
  url <- read_html(url) 
css <- (".article-body")
data <- url %>% 
  html_node(css = css) %>%
  html_text2()
}

tidy_function <- function(data){data <- str_replace_all(data, "\n", "####") %>%
  str_replace_all("/n", "####") %>%
  str_remove_all("/n") %>%
  str_remove_all("\n") %>%
  str_remove_all(" - ") %>%
  str_replace_all("'\'", "#") %>%
  str_replace_all("[0-9] of [0-9]To buy official Arsenal pictures visit Arsenal Pics", "#") %>%
  str_remove("WHAT HAPPENED") %>%
  str_remove_all("[0-9] of 42To buy official Arsenal pictures visit Arsenal Pics") %>%
  str_remove_all("[0-9] of 29To buy official Arsenal pictures visit Arsenal Pics") %>%
  str_remove_all("[0-9] of 45To buy official Arsenal pictures visit Arsenal Pics") %>%
  str_remove_all("[0-9] of 38To buy official Arsenal pictures visit Arsenal Pics") %>%
  str_remove_all("[0-9] of 32To buy official Arsenal pictures visit Arsenal Pics") %>%
  str_remove_all("[0-9] of 36To buy official Arsenal pictures visit Arsenal Pics") %>%
  str_remove("Play videoWatch Arsenal video online05:24Highlights | Crystal Palace 0-2 Arsenal - bitesize") %>%
  str_remove("111111111122222222223333333333444") %>%
  str_remove("111111111122222222223333333") %>%
  str_remove("11111111112222222222") %>%
  str_remove_all("\\(") %>%
  str_remove_all("\\)") %>%
  str_replace_all("||", "#") %>%
  str_remove_all("'Play videoWatch Arsenal video online02:17Mikel Arteta post-match interview | Crystal Palace 0-2 Arsenal | Premier LeagueArteta: \'") %>%
  str_remove_all("\"read everything from his press conferencePlay videoWatch Arsenal video online02:07William Saliba post-match interview || Premier LeagueSaliba:") %>%
  str_remove_all("#") %>%
  unlist()
}

# Running the tidy function twice to clean up certain parts that are getting missed the first time for some reason and this is a temporary fix.
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2022-Aug-05/crystal-palace-0-2-arsenal-match-report"
Match_1 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_1 <- tidy_function(Match_1)
Match_1 <- tidy_function(Match_1)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2022-Aug-13/arsenal-4-2-leicester-city-match-report"
Match_2 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_2 <- tidy_function(Match_2)
Match_2 <- tidy_function(Match_2)
Arsenal_url <- "https://www.arsenal.com/premier-league-match-report-bournemouth-odegaard-saliba-jesus"
Match_3 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_3 <- tidy_function(Match_3)
Match_3 <- tidy_function(Match_3)
Arsenal_url <- "https://www.arsenal.com/premier-league-match-report-fulham-odegaard-gabriel"
Match_4 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_4 <- tidy_function(Match_4)
Match_4 <- tidy_function(Match_4)
Arsenal_url <- "https://www.arsenal.com/match-report-aston-villa-premier-league-martinelli-jesus"
Match_5 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_5 <- tidy_function(Match_5)
Match_5 <- tidy_function(Match_5)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2022-Sep-04/manchester-united-3-1-arsenal-match-report"
Match_6 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_6 <- tidy_function(Match_6)
Match_6 <- tidy_function(Match_6)
Arsenal_url <- "https://www.arsenal.com/premier-league-match-report-brentford-saliba-jesus-vieira"
Match_7 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_7 <- tidy_function(Match_7)
Match_7 <- tidy_function(Match_7)
# Arsenal 2021 season 

Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Jul-28/arsenal-4-1-watford-match-report"
Match_1_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_1_2021 <- tidy_function(Match_1_2021)
Match_1_2021 <- tidy_function(Match_1_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Aug-01/arsenal-1-2-chelsea-match-report"
Match_2_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_2_2021 <- tidy_function(Match_2_2021)
Match_2_2021 <- tidy_function(Match_2_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Aug-08/tottenham-hotspur-1-0-arsenal-match-report"
Match_3_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_3_2021 <- tidy_function(Match_3_2021)
Match_3_2021 <- tidy_function(Match_3_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Aug-13/brentford-fc-2-0-arsenal-match-report"
Match_4_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_4_2021 <- tidy_function(Match_4_2021)
Match_4_2021 <- tidy_function(Match_4_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Aug-22/arsenal-0-2-chelsea-match-report"
Match_5_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_5_2021 <- tidy_function(Match_5_2021)
Match_5_2021 <- tidy_function(Match_5_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Aug-28/manchester-city-5-0-arsenal-match-report"
Match_6_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_6_2021 <- tidy_function(Match_6_2021)
Match_6_2021 <- tidy_function(Match_6_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Sep-11/arsenal-1-0-norwich-city-match-report"
Match_7_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_7_2021 <- tidy_function(Match_7_2021)
Match_7_2021 <- tidy_function(Match_7_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Sep-18/burnley-0-1-arsenal-match-report"
Match_8_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_8_2021 <- tidy_function(Match_8_2021)
Match_8_2021 <- tidy_function(Match_8_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Sep-26/arsenal-3-1-tottenham-hotspur-match-report"
Match_9_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_9_2021 <- tidy_function(Match_9_2021)
Match_9_2021 <- tidy_function(Match_9_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Oct-02/brighton-0-0-arsenal-match-report"
Match_10_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_10_2021 <- tidy_function(Match_10_2021)
Match_10_2021 <- tidy_function(Match_10_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Oct-18/arsenal-2-2-crystal-palace-match-report"
Match_11_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_11_2021 <- tidy_function(Match_11_2021)
Match_11_2021 <- tidy_function(Match_11_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Oct-22/arsenal-3-1-aston-villa-match-report"
Match_12_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_12_2021 <- tidy_function(Match_12_2021)
Match_12_2021 <- tidy_function(Match_12_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Oct-30/leicester-city-0-2-arsenal-match-report"
Match_13_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_13_2021 <- tidy_function(Match_13_2021)
Match_13_2021 <- tidy_function(Match_13_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Nov-07/arsenal-1-0-watford-match-report"
Match_14_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_14_2021 <- tidy_function(Match_14_2021)
Match_14_2021 <- tidy_function(Match_14_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Nov-20/liverpool-4-0-arsenal-match-report"
Match_15_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_15_2021 <- tidy_function(Match_15_2021)
Match_15_2021 <- tidy_function(Match_15_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Nov-27/arsenal-2-0-newcastle-united-match-report"
Match_16_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_16_2021 <- tidy_function(Match_16_2021)
Match_16_2021 <- tidy_function(Match_16_2021)
Arsenal_url <- "https://www.arsenal.com/arsenal-manchester-united-match-report-premier-league"
Match_17_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_17_2021 <- tidy_function(Match_17_2021)
Match_17_2021 <- tidy_function(Match_17_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Dec-06/everton-2-1-arsenal-match-report"
Match_18_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_18_2021 <- tidy_function(Match_18_2021)
Match_18_2021 <- tidy_function(Match_18_2021)
Arsenal_url <- "https://www.arsenal.com/arsenal-southampton-match-report-premier-league-lacazette"
Match_19_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_19_2021 <- tidy_function(Match_19_2021)
Match_19_2021 <- tidy_function(Match_19_2021)
Arsenal_url <- "https://www.arsenal.com/arsenal-west-ham-match-report-premier-league-martinelli-smith-rowe"
Match_20_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_20_2021 <- tidy_function(Match_20_2021)
Match_20_2021 <- tidy_function(Match_20_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Dec-18/leeds-1-4-arsenal-match-report"
Match_21_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_21_2021 <- tidy_function(Match_21_2021)
Match_21_2021 <- tidy_function(Match_21_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2021-Dec-26/norwich-city-0-5-arsenal-match-report"
Match_22_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_22_2021 <- tidy_function(Match_22_2021)
Match_22_2021 <- tidy_function(Match_22_2021)
Arsenal_url <- "https://www.arsenal.com/arsenal-manchester-city-report-xhaka-gabriel-premier-league"
Match_23_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_23_2021 <- tidy_function(Match_23_2021)
Match_23_2021 <- tidy_function(Match_23_2021)
Arsenal_url <- "https://www.arsenal.com/premier-league-burnley-match-report-emirates-stadium"
Match_24_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_24_2021 <- tidy_function(Match_24_2021)
Match_24_2021 <- tidy_function(Match_24_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2022-Feb-10/wolves-0-1-arsenal-match-report"
Match_25_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_25_2021 <- tidy_function(Match_25_2021)
Match_25_2021 <- tidy_function(Match_25_2021)
Arsenal_url <- "https://www.arsenal.com/match-report-emile-smith-rowe-bukayo-saka-premier-league-southampton"
Match_26_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_26_2021 <- tidy_function(Match_26_2021)
Match_26_2021 <- tidy_function(Match_26_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2022-Feb-24/arsenal-2-1-wolves-match-report-0"
Match_27_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_27_2021 <- tidy_function(Match_27_2021)
Match_27_2021 <- tidy_function(Match_27_2021)
Arsenal_url <- "https://www.arsenal.com/premier-league-match-report-watford-odegaard-saka-martinelli"
Match_28_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_28_2021 <- tidy_function(Match_28_2021)
Match_28_2021 <- tidy_function(Match_28_2021)
Arsenal_url <- "https://www.arsenal.com/premier-league-match-report-leicester-city-thomas-partey-alexandre-lacazette"
Match_29_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_29_2021 <- tidy_function(Match_29_2021)
Match_29_2021 <- tidy_function(Match_29_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2022-Mar-16/arsenal-0-2-liverpool-match-report"
Match_30_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_30_2021 <- tidy_function(Match_30_2021)
Match_30_2021 <- tidy_function(Match_30_2021)
Arsenal_url <- "https://www.arsenal.com/premier-league-match-report-bukayo-saka-aston-villa-top-four"
Match_31_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_31_2021 <- tidy_function(Match_31_2021)
Match_31_2021 <- tidy_function(Match_31_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2022-Apr-04/crystal-palace-3-0-arsenal-match-report"
Match_32_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_32_2021 <- tidy_function(Match_32_2021)
Match_32_2021 <- tidy_function(Match_32_2021)
Arsenal_url <- "https://www.arsenal.com/premier-league-match-report-brighton-martin-odegaard-emirates-stadium"
Match_33_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_33_2021 <- tidy_function(Match_33_2021)
Match_33_2021 <- tidy_function(Match_33_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2022-Apr-16/southampton-1-0-arsenal-match-report"
Match_34_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_34_2021 <- tidy_function(Match_34_2021)
Match_34_2021 <- tidy_function(Match_34_2021)
Arsenal_url <- "https://www.arsenal.com/match-report-premier-league-chelsea-nketiah-smith-rowe-saka"
Match_35_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_35_2021 <- tidy_function(Match_35_2021)
Match_35_2021 <- tidy_function(Match_35_2021)
Arsenal_url <- "https://www.arsenal.com/premier-league-match-report-manchester-united-saka-tavares-xhaka-ronaldo"
Match_36_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_36_2021 <- tidy_function(Match_36_2021)
Match_36_2021 <- tidy_function(Match_36_2021)
Arsenal_url <- "https://www.arsenal.com/premier-league-match-report-west-ham-london-stadium"
Match_37_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_37_2021 <- tidy_function(Match_37_2021)
Match_37_2021 <- tidy_function(Match_37_2021)
Arsenal_url <- "https://www.arsenal.com/premier-league-match-report-leeds-united-emirates-stadium-top-four-nketiah"
Match_38_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_38_2021 <- tidy_function(Match_38_2021)
Match_38_2021 <- tidy_function(Match_38_2021)
Arsenal_url <- "https://www.arsenal.com/premier-league-match-report-tottenham-hotspur-top-four"
Match_39_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_39_2021 <- tidy_function(Match_39_2021)
Match_39_2021 <- tidy_function(Match_39_2021)
Arsenal_url <- "https://www.arsenal.com/fixture/arsenal/2022-May-16/newcastle-united-2-0-arsenal-match-report"
Match_40_2021 <- Web_scrape_function_Arsenal(Arsenal_url)
Match_40_2021 <- tidy_function(Match_40_2021)
Match_40_2021 <- tidy_function(Match_40_2021)
# Manchester City data

Web_scrape_function_mancity <- function(url,css,data) { # creating function to repeat web scrape 
  url <- read_html(url) 
css <- (".article-body__article-text")
data <- url %>% 
  html_node(css = css) %>%
  html_text2()
data <- str_replace_all(data, "\n", "####") %>%
  str_replace_all("/n", "####") %>%
  str_remove_all("/n") %>%
  str_remove_all("\n") %>%
  str_remove_all(" - ") %>%
  str_remove_all("\\(") %>%
  str_remove_all("\\)") %>%
  str_remove_all("#") %>%
  unlist()
}

mancity_url <- "https://www.mancity.com/news/mens/west-ham-v-manchester-city-premier-league-match-report-63795480"
Manc_1 <- Web_scrape_function_mancity(mancity_url)

mancity_url <- "https://www.mancity.com/news/mens/man-city-bournemouth-premier-league-match-report-63795987"
Manc_2 <- Web_scrape_function_mancity(mancity_url)

mancity_url <- "https://www.mancity.com/news/mens/newcastle-v-manchester-city-match-report-63796690"
Manc_3 <- Web_scrape_function_mancity(mancity_url)

mancity_url <- "https://www.mancity.com/news/mens/man-city-crystal-palace-match-report-63797204"
Manc_4 <- Web_scrape_function_mancity(mancity_url)

mancity_url <- "https://www.mancity.com/news/mens/manchester-city-v-nottingham-forest-match-report-31-august-63797573"
Manc_5 <- Web_scrape_function_mancity(mancity_url)

mancity_url <- "https://www.mancity.com/news/mens/aston-villa-manchester-city-premier-league-match-report-63797816"
Manc_6 <- Web_scrape_function_mancity(mancity_url)

mancity_url <- "https://www.mancity.com/news/mens/wolves-manchester-city-away-premier-league-2022-match-report-63799002"
Manc_7 <- Web_scrape_function_mancity(mancity_url)

# New Castle 

# New Castle United first match against nottingham forest
# 1 rule for 1 bots crawl delay 5 seconds, scrapable

bow("https://www.nufc.co.uk/matches/first-team/2022-23/newcastle-united-v-nottingham-forest/")

Web_scrape_function_Newcastle <- function(url,css,data) { # creating function to repeat web scrape 
  url <- read_html(url) 
css <- (".article__body")
data <- url %>% 
  html_node(css = css) %>%
  html_text2()
data <- str_replace_all(data, "\n", "####") %>%
  str_replace_all("/n", "####") %>%
  str_remove_all("/n") %>%
  str_remove_all("\n") %>%
  str_remove_all(" - ") %>%
  str_remove_all("\\(") %>%
  str_remove_all("\\)") %>%
  str_remove_all("\"") %>%
  str_remove_all("#") %>%
  unlist()
}

Newcastle_url <- "https://www.nufc.co.uk/matches/first-team/2022-23/newcastle-united-v-nottingham-forest/"
nc_1 <- Web_scrape_function_Newcastle(Newcastle_url)
                        
Newcastle_url <- "https://www.nufc.co.uk/matches/first-team/2022-23/brighton-and-hove-albion-v-newcastle-united/"
nc_2 <- Web_scrape_function_Newcastle(Newcastle_url)
                        
Newcastle_url <- "https://www.nufc.co.uk/matches/first-team/2022-23/newcastle-united-v-manchester-city/"
nc_3 <- Web_scrape_function_Newcastle(Newcastle_url)
                        
Newcastle_url <- "https://www.nufc.co.uk/matches/first-team/2022-23/wolverhampton-wanderers-v-newcastle-united/"
nc_4 <- Web_scrape_function_Newcastle(Newcastle_url)
                        
Newcastle_url <- "https://www.nufc.co.uk/matches/first-team/2022-23/liverpool-v-newcastle-united/"
nc_5 <- Web_scrape_function_Newcastle(Newcastle_url)
                        
Newcastle_url <- "https://www.nufc.co.uk/matches/first-team/2022-23/newcastle-united-v-crystal-palace/"
nc_6 <- Web_scrape_function_Newcastle(Newcastle_url)
                        
Newcastle_url <- "https://www.nufc.co.uk/matches/first-team/2022-23/newcastle-united-v-bournemouth/"
nc_7 <- Web_scrape_function_Newcastle(Newcastle_url)

# Everton 

# Everton vs Chelsea
# 1 rule for 1 bots crawl delay 5 seconds, scrapable

bow("https://www.evertonfc.com/match/74913/everton-chelsea#report")

Web_scrape_function_Everton <- function(url,css,data) { # creating function to repeat web scrape 
  url <- read_html(url) 
css <- (".article__body.mc-report__body.js-article-body")
data <- url %>% 
  html_node(css = css) %>%
  html_text2()
data <- str_replace_all(data, "\n", "####") %>%
  str_replace_all("/n", "####") %>%
  str_remove_all("/n") %>%
  str_remove_all("\n") %>%
  str_remove_all(" - ") %>%
  str_remove_all("\\(") %>%
  str_remove_all("\\)") %>%
  str_remove_all("\"") %>%
  str_remove_all("#") %>%
  unlist()
}

Everton_url <- "https://www.evertonfc.com/match/74913/everton-chelsea#report"
ever_1 <- Web_scrape_function_Everton(Everton_url)

Everton_url <- "https://www.evertonfc.com/match/74922/aston-villa-everton#report"
ever_2 <- Web_scrape_function_Everton(Everton_url)

Everton_url <- "https://www.evertonfc.com/match/74933/everton-nottm-forest#report"
ever_3 <- Web_scrape_function_Everton(Everton_url)

Everton_url <-"https://www.evertonfc.com/match/74943/brentford-everton#report"
ever_4 <- Web_scrape_function_Everton(Everton_url)

Everton_url <- "https://www.evertonfc.com/match/74955/leeds-everton#report"
ever_5 <- Web_scrape_function_Everton(Everton_url)

Everton_url <- "https://www.evertonfc.com/match/74965/everton-liverpool#report"
ever_6 <- Web_scrape_function_Everton(Everton_url)

Everton_url <- "https://www.evertonfc.com/match/74985/everton-west-ham#report"
ever_7 <- Web_scrape_function_Everton(Everton_url)

# Leicester 

# Leicester against Brentford
# 1 bot 1 rule scrapable 5 second crawl
bow("https://www.lcfc.com/news/2729025/city-held-by-bees-in-premier-league-opener/featured")

Web_scrape_function_Leicester <- function(url,css,data) { # creating function to repeat web scrape 
  url <- read_html(url) 
css <- (".col-12")
data <- url %>% 
  html_node(css = css) %>%
  html_text2()
data <- str_replace_all(data, "\n", "####") %>%
  str_replace_all("/n", "####") %>%
  str_remove_all("/n") %>%
  str_remove_all("\n") %>%
  str_remove_all(" - ") %>%
  str_remove_all("\\(") %>%
  str_remove_all("\\)") %>%
  str_remove_all("\"") %>%
  str_remove_all("#") %>%
  str_remove_all("More on this story. . . In Photos -") %>%
  unlist()
}

Leicester_url <- "https://www.lcfc.com/news/2729025/city-held-by-bees-in-premier-league-opener/featured"
lei_1 <- Web_scrape_function_Leicester(Leicester_url)

Leicester_url <- "https://www.lcfc.com/news/2739798/foxes-fall-to-defeat-at-arsenal/featured"
lei_2 <- Web_scrape_function_Leicester(Leicester_url)

Leicester_url <- "https://www.lcfc.com/news/2751347/saints-take-the-points-on-filbert-way/featured"
lei_3 <- Web_scrape_function_Leicester(Leicester_url)

Leicester_url <- "https://www.lcfc.com/news/2762326/city-defeated-as-10man-chelsea-win-at-stamford-bridge/featured"
lei_4 <- Web_scrape_function_Leicester(Leicester_url)

Leicester_url <- "https://www.lcfc.com/news/2774578/man-utd-defeat-for-leicester-on-matchday-five/featured"
lei_5 <- Web_scrape_function_Leicester(Leicester_url)

Leicester_url <- "https://www.lcfc.com/news/2779658/city-beaten-away-to-brighton/featured"
lei_6 <- Web_scrape_function_Leicester(Leicester_url)

Leicester_url <- "https://www.lcfc.com/news/2793845/leicester-lose-to-spurs-in-london/featured"
lei_7 <- Web_scrape_function_Leicester(Leicester_url)

# West Ham 

# West Ham vs Manchester City

Web_scrape_function_WestHam <- function(url,css,data) { # creating function to repeat web scrape 
  url <- read_html(url) 
css <- (".m-article__columns")
data <- url %>% 
  html_node(css = css) %>%
  html_text2()
data <- str_replace_all(data, "\n", "####") %>%
  str_replace_all("/n", "####") %>%
  str_remove_all("/n") %>%
  str_remove_all("\n") %>%
  str_remove_all(" - ") %>%
  str_remove_all("\\(") %>%
  str_remove_all("\\)") %>%
  str_remove_all("\"") %>%
  str_remove_all("#") %>%
  str_remove_all("More on this story. . . In Photos -") %>%
  unlist()
}

WestHam_url <- "https://www.whufc.com/fixture/view/6472"
wh_1 <- Web_scrape_function_WestHam(WestHam_url)

WestHam_url <- "https://www.whufc.com/fixture/view/6464"
wh_2 <- Web_scrape_function_WestHam(WestHam_url)

WestHam_url <- "https://www.whufc.com/fixture/view/6452"
wh_3 <- Web_scrape_function_WestHam(WestHam_url)

WestHam_url <- "https://www.whufc.com/fixture/view/6450"
wh_4 <- Web_scrape_function_WestHam(WestHam_url)

WestHam_url <- "https://www.whufc.com/fixture/view/6436"
wh_5 <- Web_scrape_function_WestHam(WestHam_url)

WestHam_url <- "https://www.whufc.com/fixture/view/6428"
wh_6 <- Web_scrape_function_WestHam(WestHam_url)

WestHam_url <- "https://www.whufc.com/fixture/view/6407"
wh_7 <- Web_scrape_function_WestHam(WestHam_url)
```

# Preprocessing

```{r}


# First step is to make these character vectors into a corpus to use for preprocessing 
# Arsenal
Arsenal <- c(Match_1, Match_2, Match_3, Match_4, Match_5, Match_6, Match_7,Match_1_2021, Match_2_2021, Match_3_2021, Match_4_2021, Match_5_2021, Match_6_2021, Match_7_2021,Match_8_2021, Match_9_2021, Match_10_2021, Match_11_2021, Match_12_2021, Match_13_2021, Match_14_2021, Match_15_2021, Match_16_2021, Match_17_2021, Match_18_2021, Match_19_2021, Match_20_2021, Match_21_2021, Match_22_2021, Match_23_2021, Match_24_2021, Match_25_2021, Match_26_2021, Match_27_2021, Match_28_2021, Match_29_2021, Match_30_2021, Match_31_2021, Match_32_2021, Match_33_2021, Match_34_2021, Match_35_2021, Match_36_2021, Match_37_2021, Match_38_2021, Match_39_2021, Match_40_2021)

Arsenal_corpus <- corpus(Arsenal)
# Man city

Manchester_City <- c(Manc_1, Manc_2, Manc_3, Manc_4, Manc_5, Manc_6, Manc_7)
                        

# Newcastle united

Newcastle_United <- c(nc_1, nc_2, nc_3, nc_4, nc_5, nc_6, nc_7)

# Everton

Everton <- c(ever_1, ever_2, ever_3, ever_4, ever_5, ever_6, ever_7)

# Leicester

Leicester <- c(lei_1, lei_2, lei_3, lei_4, lei_5, lei_6, lei_7)

# West Ham

West_Ham_United <- c(wh_1, wh_2, wh_3, wh_4, wh_5, wh_6, wh_7)

# Creating list of objects to put into the loop
Prem <- c("Arsenal", "Manchester_City", "Newcastle_United", "Everton", "Leicester", "West_Ham_United")


# create loop.
for (i in 1:length(Prem)){
  
  # create corpora
  corpusCall <- paste(Prem[i],"_corpus <- corpus(",Prem[i],")", sep = "")
    #print(corpusCall)
  eval(parse(text=corpusCall))
   #print(corpusCall)

  # change document names for each chapter to include the book title. If you don't do this, the document names will be duplicated and you'll get an error.
  namesCall <- paste("tmpNames <- docnames(",Prem[i],"_corpus)", sep = "")
  eval(parse(text=namesCall))
  print(namesCall)
  bindCall <- paste("docnames(",Prem[i],"_corpus) <- paste(\"",Prem[i],"\", tmpNames, sep = \"-\")", sep = "")
  eval(parse(text=bindCall))
  print(bindCall)
  # create summary data
  summaryCall <- paste(Prem[i],"_summary <- summary(",Prem[i],"_corpus)", sep = "")
  eval(parse(text=summaryCall))

  # add indicator
  bookCall <- paste(Prem[i],"_summary$Team <- \"",Prem[i],"\"", sep = "")
  eval(parse(text=bookCall))

  # add chapter indicator
  chapterCall <- paste(Prem[i],"_summary$Match <- as.numeric(str_extract(",Prem[i],"_summary$Text, \"[0-9]+\"))", sep = "")
  eval(parse(text=chapterCall))

  # add meta data to each corpus
  metaCall <- paste("docvars(",Prem[i],"_corpus) <- ",Prem[i],"_summary", sep = "")
  eval(parse(text=metaCall))

}

Prem <- c(Arsenal_corpus, Manchester_City_corpus, Newcastle_United_corpus, Everton_corpus, Leicester_corpus, West_Ham_United_corpus)

Prem_summary <- summary(Prem)
ndoc(Prem)

Arsenal_1 <- corpus_subset(Prem, Team == 'Arsenal')

summary(Arsenal_1)


Prem_dfm <- dfm(tokens(Prem,
remove_punct = TRUE,
remove_symbols = TRUE) %>%
dfm(tolower = TRUE) %>%
dfm_remove(stopwords('english')))

topfeatures(Prem_dfm, 20)

set.seed(1)

# Creating a table to show the highest frequency items and then ranking them
word_counts <- as.data.frame(sort(colSums(Prem_dfm),dec=T))
colnames(word_counts) <- c("Frequency")
word_counts$Rank <- c(1:ncol(Prem_dfm))

ggplot(word_counts, mapping = aes(x = Rank, y = Frequency)) + 
  geom_point() +
  labs(title = "Zipf's Law", x = "Rank", y = "Frequency") + 
  theme_bw()

Prem_smaller_dfm <- dfm_trim(Prem_dfm, min_termfreq = 10)

# trim based on the proportion of documents that the feature appears in; here, 
# the feature needs to appear in more than 10% of documents (chapters)
Prem_smaller_dfm <- dfm_trim(Prem_smaller_dfm, min_docfreq = 0.1, docfreq_type = "prop")

Prem_smaller_dfm

textplot_wordcloud(Prem_smaller_dfm, min_count = 50,
                   random_order = FALSE)


# Creating the FCM

Prem_smaller_dfm <- dfm_trim(Prem_dfm, min_termfreq = 20)
Prem_smaller_dfm <- dfm_trim(Prem_smaller_dfm, min_docfreq = .3, docfreq_type = "prop")

# create fcm from dfm
Prem_smaller_fcm <- fcm(Prem_smaller_dfm)

# check the dimensions (i.e., the number of rows and the number of columnns)
# of the matrix we created
dim(Prem_smaller_fcm)

# pull the top features
myFeatures <- names(topfeatures(Prem_smaller_fcm, 30))

# retain only those top features as part of our matrix
Prem_smaller_fcm <- fcm_select(Prem_smaller_fcm, pattern = myFeatures, selection = "keep")

# compute size weight for vertices in network
size <- log(colSums(Prem_smaller_fcm))

# create plot
textplot_network(Prem_smaller_fcm, vertex_size = size / max(size) * 3)
```