---
title: "Blog Post 6"
author: "Claire Battaglia"
desription: "STM, continued"
date: "12/04/2022"
format:
  html:
    toc: true
    code-fold: true
    code-copy: true
    code-tools: true
categories:
  - Claire Battaglia
  - text-as-data
  - blog post 6
  - open-text survey response
  - unsupervised learning
  - topic models
  - causal inference
---

```{r}
#| label: setup
#| warning: false

library(readxl)
library(plyr)
library(tidyverse)
library(tidytext)
library(quanteda)
library(quanteda.textplots)
library(gmodels)
library(stm)

knitr::opts_chunk$set(echo = TRUE)
```

For this final blog post I will be exploring Structural Topic Modeling (STM) further and thinking about causal inference in the context of my research question and hypotheses.

After thinking about my dataset and research question further, I have decided to consider some additional covariates so I'll begin with reworking my dataset, corpus, and Document Feature Matrix to include those covariates. Then I'll explore other values for $k$ and spend some time thinking about the substantive interpretation of my results.

## Creating My Corpus

Instead of messing around with the code in my previous blog posts, I will create a new tidy dataset with the additional covariates I'm going to include and a new corpus and Document Feature Matrix (DFM) from which to work.

```{r tidy dataset}
# read data
CFA_raw <- read_excel("FPAB Community Food Assessment Survey Data.xlsx", sheet = "Raw")

# rename columns
CFA_tidy_final <- CFA_raw %>%
  rename("id" = "Respondent ID",
         "zip" = "Zip Code",
         "age" = "Age",
         "income" = "Annual Household Income",
         "size" = "Number of Individuals in Your Household",
         "change" = "What changes would you like to see for Missoula’s food system?")

# create subset
CFA_tidy_final <- CFA_tidy_final %>%
  subset(select = c("zip", "age", "income", "size", "change"))

# change class
CFA_tidy_final$zip <- as.character(CFA_tidy_final$zip)
CFA_tidy_final$age <- as.numeric(CFA_tidy_final$age)
CFA_tidy_final$size <- as.numeric(CFA_tidy_final$size)

# remove na values
CFA_tidy_final <- na.omit(CFA_tidy_final)

# save
save(CFA_tidy_final, file = "CFA_tidy_final.RData")
```

I now have a new tidy dataset that includes 4 covariates:

1. age of respondent (age)
2. number of people living in the household (size)
3. annual household income bracket (income)
4. ZIP code in which household of respondent is located (zip)

```{r create dfm}
# remove row where change = ?
CFA_tidy_final <- subset(CFA_tidy_final, change !="?")

# create dfm
dfm_change_final <- dfm(tokens(CFA_tidy_final$change),
             tolower = TRUE,
             remove = stopwords("en"),
             remove_punct = TRUE)

# get dimensions
dim(dfm_change_final)
```

My new DFM contains 208 rows (the responses) and 1,125 columns (all the words that appear in the corpus).

```{r covariate frequency}
# frequency counts for covariates
table(CFA_tidy_final$age) # age
table(CFA_tidy_final$size) # size
table(CFA_tidy_final$income) # income
table(CFA_tidy_final$zip) # zip
```

This is a horrible way to try and understand frequency and distribution so I'll create some simple visualizations to make this information more accessible.

```{r visualize covariate frequency}
# create hist - age
ggplot(CFA_tidy_final, aes(x = age)) +
  geom_histogram(fill = "#830042") +
  labs(title = "Respondent Age", x = "Age", y = NULL) +
  coord_flip() +
  theme_minimal()

# create hist - size
ggplot(CFA_tidy_final, aes(x = size)) +
  geom_histogram(fill = "#830042") +
  labs(title = "Number of People Living in Household", x = "Number of People", y = NULL) +
  coord_flip() +
  theme_minimal()

# create bar plot - income
ggplot(CFA_tidy_final, aes(x = income)) +
  geom_bar(fill = "#830042") +
  labs(title = "Annual Household Income Bracket of Respondent", x = "Income Bracket", y = NULL) +
  coord_flip() +
  theme_minimal()

# create bar plot - zip
ggplot(CFA_tidy_final, aes(x = zip)) +
  geom_bar(fill = "#830042") +
  labs(title = "ZIP Code of Household", x = "Zip Code", y = NULL) +
  coord_flip() +
  theme_minimal()
```

These are very simple but they give a much better sense of the distribution of respondents across each covariate.

It seems that most respondents:

* Are between 30 and 60 years old
* Live in 2-person households
* Have an annual household income between $50,000-250,000
* Live in 59801, 59802, 59802 (3 of the central ZIP codes in the City of Missoula)

## Document Feature Matrix

Next I'll visualize my DFM with a word cloud.

```{r wordcloud}
# create wordcloud
# png(filename = "dfm_change_final_WORD.png")
textplot_wordcloud(dfm_change_final, min_count = 5, max_words = 50, random_order = FALSE)
# dev.off()
```

## Structured Topic Model(s)

Now I am ready to construct my Structured Topic Model(s). As I mentioned above, I'll be exploring different values for $k$, as well as thinking about the substantive interpretation of my models.

```{r searchK}
# searchK
differentKs <- searchK(dfm_change_final,
                       K = c(3, 5, 7),
                       prevalence = ~ age + size + income + zip,
                       N = 208,
                       data = CFA_tidy_final,
                       max.em.its = 1000,
                       init.type = "Spectral")

# diagnostic plots
plot(differentKs)
```
The plot of Held-Out Likelihood would lead us to the 3-topic model. The plot of Semantic Coherence would lead us to the 7-topic model. The Residuals plot would also lead us to the 7-topic model. These are not as conclusive as I was hoping they would so, given that, I am going to construct all 3 models.

```{r construct stm}
# model w/ 3 topics
stm_change_final_3 <- stm(dfm_change_final,
               K = 3,
               prevalence = ~ age + size + income + zip,
               data = CFA_tidy_final,
               max.em.its = 1000,
               seed = 1234,
               init.type = "Spectral")

# model w/ 5 topics
stm_change_final_5 <- stm(dfm_change_final,
               K = 5,
               prevalence = ~ age + size + income + zip,
               data = CFA_tidy_final,
               max.em.its = 1000,
               seed = 1234,
               init.type = "Spectral")

# model w/ 7 topics
stm_change_final_7 <- stm(dfm_change_final,
               K = 7,
               prevalence = ~ age + size + income + zip,
               data = CFA_tidy_final,
               max.em.its = 1000,
               seed = 1234,
               init.type = "Spectral")
```

```{r label topics and plot}
# label topics - 3 topics
labelTopics(stm_change_final_3)
plot(stm_change_final_3, type = "summary") # plot

# label topics - 5 topics
labelTopics(stm_change_final_5)
plot(stm_change_final_5, type = "summary") # plot

# label topics - 7 topics
labelTopics(stm_change_final_7)
plot(stm_change_final_7, type = "summary") # plot
```
Looking at these plots, I am leaning towards the 7-topic model because the topics appear to be more strongly differentiated from one another. While most of the topics revealed by all 3 models feature the words "food" and "local," in the 7-topic model the third word for each topic is distinct enough to give me a sense of that topic. For example, "education" (Topic 1) and "gardens" (Topic 7) are distinct concepts.

```{r}
topic_names <- labelTopics(stm_change_final_7, n=4)$frex
topic_labels <- rep(NA, 7)
for (i in 1:7) {
  topic_labels[i] <- paste(topic_names[i,], collapse = "_")
}

print(topic_labels)
```

Moving ahead with the 7-topic model, I will now estimate the effects of my covariates on topic prevalence.

```{r estimate effects}
# estimate effects
effects_estimate <- estimateEffect(formula = 1:7 ~ age + size + income + zip,
                                   stmobj = stm_change_final_7,
                                   metadata = CFA_tidy_final)

# get summary
summary(effects_estimate)
```

Topic 1: county_facilities_year_production

* Has a statistically significant, positive association with *ZIP code* 59868.

Topic 2: ag_stores_cost_produce

* Has no statistically significant (at the .01 level) association with any covariates.

Topic 3: enough_growing_market_grow

* Has a statistically significant, negative association with every *ZIP code*.

Topic 4: organic_less_produced_sourced

* Has no statistically significant association with any covariates.

Topic 5: affordable_composting_new_healthy

* Has a statistically significant, positive association with number of people living in household (*size*).

Topic 6: preserve_prices_farm_development

* Has a statistically significant, positive association with *ZIP code* 59821.

Topic 7: restaurants_producers_gardens_city

* Has a statistically significant, negative association with *age* and a statistically significant, positive association with *ZIP code* 59908.


## Conclusion

I still need to spend some time thinking about these topics and results but my analysis is taking shape!
