---
title: "Blog Post 3"
author: "Claire Battaglia"
desription: "Blog Post 3"
date: "10/16/2022"
format:
  html:
    toc: true
    code-fold: true
    code-copy: true
    code-tools: true
categories:
  - Claire Battaglia
  - text-as-data
  - blog post 3
  - open-text survey response
  - Document Term Matrix
---

```{r}
#| label: setup
#| warning: false

library(readxl)
library(plyr)
library(tidyverse)
library(tidytext)
library(quanteda)
library(quanteda.textplots)

knitr::opts_chunk$set(echo = TRUE)
```

```{r load data}
# load tidy data from blog post 2
load("CFA_tidy.RData")
```

## Creating My Corpus

I am most interested in the question "What changes would you like to see for Missoula’s food system?" so I'll start there. First I'll create a corpus of the responses.

```{r create corpus}
# create corpus for "change"
change_corpus <- corpus(CFA_tidy$change)

# save
save(change_corpus, file = "change_corpus.RData")

# get summary
change_summary <- summary(change_corpus)

# add indicator (not sure I need this but it won't hurt)
change_summary$question <- "change"

# preview
head(change_summary)
```

I have created a corpus of the responses in which each text is an individual response. The summary shows how many types, tokens, and sentences are in each response. This is utterly uninteresting information for this particular corpus and research question but it's good to practice.

## Pre-Processing Decisions

Next I need to make some decisions about pre-processing. Some options include:

* Remove capitalization. - *I don't see any reason not to.*
* Remove punctuation. - *Again, I don't see any reason not to.*
* Remove stop words. - *I will probably want to remove stop words but I am going to examine the list and may customize it.*
* Remove numbers. - *I am not going to remove numbers. The question, especially in the larger context of the survey, could easily yield responses that contain numbers that are meaningful.*
* Stem - *Stemming makes me nervous and I don't see any reason it would be necessary so I am not going to stem.*
* Infrequently used terms - *Not sure about this yet.*
* N-grams - *Not sure about this yet.*

```{r tokenize}
# tokenize
change_tokens <- tokens(change_corpus, 
    remove_punct = T) # remove punctuation
change_tokens <- tokens_tolower(change_tokens) # remove capitalization

save(change_tokens, file = "change_tokens.RData")

# view
print(change_tokens)
```

Things I'm thinking about right now:

* Would it be meaningful to/how could I capture frequency of concept "more or less" of something? Could I sort everything respondents want more or less of into broad categories? I.e. 75% of respondents want more of something. Of those that want more of something, 35% want more education, 10% want more food assistance benefits, etc. Is this what STM allows me to do?

## Document Feature Matrix

```{r document feature matrix}
# create document feature matrix
change_dfm <- dfm(change_tokens)

save(change_dfm, file = "change_dfm.RData")

# view
print(change_dfm)
```

Again, this yields an enormous volume of uninteresting, unsurprising data (part of the reason is likely that I haven't removed any stopwords yet).

```{r working with the dfm}
# get 10 most frequent terms
topfeatures(change_dfm, 10)
```

I'm going to create a separate object for my corpus with the stopwords removed so that I can compare the document feature matrices and most frequent words side-by-side.

```{r create new object with no stopwords}
# create new object
change_tokens_no_stop <- tokens_select(change_tokens,
                                       pattern = stopwords("en"),
                                       selection = "remove")
# create new dfm
change_no_stop_dfm <- dfm(change_tokens_no_stop)

save(change_no_stop_dfm, file = "change_no_stop_dfm.RData")

# get 10 most frequent terms
topfeatures(change_no_stop_dfm, 10)
```

Hmm, interesting. Much more informative but some of the most frequent words are 1) completely expected, and 2) not substantively meaningful on their own.

For example, I would expect "food" to be mentioned frequently but without any sense of what the respondent has said about it, it's not meaningful. The survey is about the food system so their answer *should* have something to do with food.

I'll need to think about this more.

Just for fun, though, I'll create a word cloud of the 10 most frequent terms.

```{r wordcloud}
# create wordcloud
textplot_wordcloud(change_no_stop_dfm, min_count = 5, max_words = 50, random_order = FALSE)
```


